---
title: "Week 5 Visualizations Activity"
author: "Mahsa Karkhaneh"
date: '2022'
output: 
  html_document:
    theme: 
      bootswatch: darkly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(bslib)
library(dplyr)
library(ggplot2)
```

We have data about cases where police have killed Americans in 2015.

```{r police_killing , echo=FALSE}
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/police-killings/police_killings.csv"
police_killing <- read_csv(url)
police_killing<- as.data.frame(police_killing)
# I used read_csv() and as.data.frame() in order to read and consider data set as a data frame to R, respectively. 
```

```{r, echo=FALSE}
mydata <-  police_killing %>% 
  select(name,age,gender,raceethnicity,city,state,pop,h_income,county_income,comp_income)
```

This data set has `r nrow(mydata)` rows and `r ncol(mydata)` columns.
.The names of the columns and a brief description are in the table below:

``` {r, echo = FALSE}
text_tbl <- data.frame(Names=c("name","age","gender","raceethnicity","city","state","pop","h_income","county_income","comp_income"),Description=c("Name of deceased","Age of deceased","Gender of deceased","Race/ethnicity of deceased","City where incident occurred","State where incident occurred","Tract population","Tract-level median household income","County-level median household income","h_income / county_income"))
text_tbl

```

In following plot we can compare the deceased based on race ethnicity :

```{r, echo=FALSE}
mydata %>% 
  ggplot(aes(fct_infreq(raceethnicity)%>% fct_rev())) + 
  geom_bar()+coord_flip()+labs(x="deceased race")
```

Following Histogram indicates that majority of deceased has a  household income less than 50,000 yearly.

```{r, echo=FALSE}
ggplot(mydata, aes(h_income)) +
  geom_histogram()
```

```{r, echo=FALSE}
low_income <- mydata %>% 
  filter(comp_income < 0.5 )
```

Assumed that “low-income” earners are people whose household income is less than half of County-level median household, so We have   `r nrow(low_income)` deceased that are low income. The distribution is shown
below: 

```{r, echo=FALSE}
low_income %>% 
  ggplot(aes(comp_income)) + 
  geom_freqpoly(binwidth = 0.01)
```

Also following bar chart shows most of deceased are male :

```{r, echo=FALSE}
mydata %>% 
  ggplot(aes(fct_infreq(gender)%>% fct_rev())) + 
  geom_bar()+coord_flip()+labs(x="deceased gender")
```
